RDF Validation of \\ Metadata on Highly-Complex Person-Level Data Sets

### 2015-01-10 paper/paper6/paper6.tex
RDF Data Cube constraints

@@

\author[gesis]{Thomas Bosch\corauthref{C}},
\ead{thomas.bosch@gesis.org}
\author[gesis]{Benjamin Zapilko},
\ead{benjamin.zapilko@gesis.org}
\author[gesis]{Joachim Wackerow}
\ead{joachim.wackerow@gesis.org}
\author[mannheim]{Kai Eckert}
\ead{kai@informatik.uni-mannheim.de}

@@

\section{Introduction}
\label{introduction}

>>>>

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\bz}[1]{\todo[size=\small, color=red!40]{\textbf{Ben:} #1}}
\newcommand{\jw}[1]{\todo[size=\small, color=blue!40]{\textbf{Achim:} #1}}

@@

\author[gesis]{Thomas Bosch\corauthref{C}},
\ead{thomas.bosch@gesis.org}
\author[gesis]{Benjamin Zapilko},
\ead{benjamin.zapilko@gesis.org}
\author[gesis]{Joachim Wackerow}
\ead{joachim.wackerow@gesis.org},
\author[mannheim]{Kai Eckert}
\ead{kai@informatik.uni-mannheim.de}

@@

\section{Motivation}

\begin{itemize}
	\item Why do we need RDF Validation?
	\item Why do we need to validate metadata on person-level data sets? 
\end{itemize}

\section{Data Documentation Initiative}

\section{DDI-RDF Discovery Vocabulary}

\begin{itemize}
  \item overview of disco
	\item description of disco
\end{itemize}

\subsection{Conceptional Model}

\subsection{Use Cases}

\subsection{Relationships to other Vocabularies}

\begin{itemize}
	\item RDF Data Cube, DCAT, PHDD, XKOS
	\item brief description of vocabularies
\end{itemize}

\section{Validation of Metadata on Person-Level Data Sets}

\subsection{Qualified Cardinality Restrictions}

\section{Validation in Combination with other Vocabularies}

\subsection{RDF Data Cube Vocabulary}

There are 22 RDF Data Cube integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} \cite{CyganiakReynolds2014}.

\textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}

\textbf{Datatypes.}
\begin{itemize}
	\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
\end{itemize}

\textbf{Unqualified Cardinality Restrictions.}
\begin{itemize}
	\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}.  
\end{itemize}

\textbf{Qualified Cardinality Restrictions.}
\begin{itemize}
	\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
	\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
	\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
\end{itemize}

\textcolor{blue}{are there further constraints which can be described in this paper?}

\subsection{SKOS and XKOS}

\subsection{PHDD}

\section{Implementation}

\textbf{Validation of Data Cube instances.}
\begin{itemize}
	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
\end{itemize}

\section{Related Work}

\textbf{RDF Data Cube Vocabulary.}
A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
\cite{CyganiakReynolds2014}

\section{Conclusion and Future Work}
